Multisensor Architecture for an Intersection Management System

### 2018-08-17 ch1-introduction.tex
Corrections in ch 1, 2 and 5

Traditionally, the vision of transport systems has been constrainted to the set of elements belonging to infrastructure and the vehicles using it. As population increases and cities growth, the number of vehicles going through world roads also increases, but the growth rate of road network is lower. This situation leads to low quality in transportation; congestion and collisions affect movility in all cities in the world and develop of efficient and long-lasting solutions carries high costs.

One of the critical places where is imperative to improve safety and efficiency are vehicular intersections, because at these points many vehicles with different directions and speeds meet each other, increasing probability of incidents. Almost 40 percent of traffic accidents reported in US in 2008, were intersection related \cite{Choi2010}. In Colombia, at 2011 most of accidents in main cities were at intersections \cite{CorporacionFondodePrevencionVial2010}.

@@

Chapter 3 presents the result of two example implementations using the architecture: Only camera case and multiple laser and camera case. For the later, 4 different fusion strategies are evaluated. These test cases are implemented and compared using traffic flow status as comparison indicator.

>>>>

Traditionally, the vision of transport systems has been constrainted to the set of elements belonging to infrastructure and the vehicles using it. As population increases and cities growth, the number of vehicles using roads also increases, but the growth rate of road network is lower. This situation leads to low quality in transportation; congestion and collisions affect movility in all cities in the world and development of efficient and long-lasting solutions carries high costs.

One of the critical places where is imperative to improve safety and efficiency is at vehicular intersections, because at these points many vehicles with different directions and speeds meet each other, increasing probability of incidents. Almost 40 percent of traffic accidents reported in US in 2008, were intersection related \cite{Choi2010}. In Colombia, at 2011 most of accidents in main cities were at intersections \cite{CorporacionFondodePrevencionVial2010}.

@@

Chapter 3 presents the result of two test implementations using the proposed architecture: 1) Using one camera and 2) Using multiple laser and one camera. For the later, 4 different fusion strategies are evaluated. These test cases are implemented and compared using traffic flow status as comparison indicator.

### 2018-08-17 ch5-conclusions.tex
Corrections in ch 1, 2 and 5

%ch5-conclusions
\chapter {Conclusions}

%\section{General Conclusions}

@@

On the other side, a couple of articles are being reviewed previous to be submmited to a journal. One article is  a review on intersection management systems, based on chapter 1 and another for architecture description and example implementation , based on chapters 2 and 3.

>>>>

%ch5-conclusions
\chapter[Conclusions]{Conclusions}

\epigraph{"If you can't explain it simply, you don't understand it well enough"}{Albert Einstein}
%\section{General Conclusions}

@@

On the other side, a couple of articles are being reviewed previous to be submmited to a journal. One article is a review on intersection management systems, based on chapter 1 and another for architecture description and example implementation, based on chapters 2 and 3.

### 2018-08-17 main.tex
Ch5 ok. Update.
Corrections and figures updated.
Corrections in ch 1, 2 and 5

%
\documentclass{book}

@@

@@

@@

\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}%
Intersections or juntions are critical points in transportation systems due to their dynamic nature, making them prone to safety or efficiency problems. For this reason the use of technology in monitoring intersections have been increasing over the last years. After a comprehensive review on this topic, a  multisensor architecture for an intersection management system is conceived, having as main features its scalability and modularity. This architecture is composed by 4 main elements: communication structure, data model, information structure and processing blocks. An example implementation of the architecture is made using the publisher/subscriber approach along with different tools and technologies that allow the whole system to fulfill the proposed criteria, to be scalable and modular. After testing the system using a dataset containing data from camera sensors and lasers sensors, some comments about its results, future developments and integration with current needs and new trends, are discussed.

>>>>

%\documentclass[draft]{book}
\documentclass{book}

@@

\newcommand\MyBox[2]{
  \fbox{\lower0.75cm
    \vbox to 1cm{\vfil
      \hbox to 1cm{\hfil\parbox{1.1cm}{#1\\#2}\hfil}
      \vfil}%
  }%
}

@@

\input{last_version}

@@

\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}%
Intersections or junctions are critical points in transportation systems due to their dynamic behaviour, making them prone to safety or efficiency problems. For this reason the use of technology in monitoring intersections has increased over the last years. After a comprehensive review on this topic, a  multisensor architecture for an intersection management system is conceived, having as main features its scalability and modularity. This architecture is composed by four main elements: communication structure, data model, information structure and processing blocks. An example implementation of the architecture is made using the publisher/subscriber approach along with different tools and technologies that allow the whole system to fulfill the proposed criteria, to be scalable and modular. After testing the system using a dataset containing data from camera sensors and lasers sensors, it has been found that the use of heterogeneous data can lead to better results, at a low cost in complexity using the proposed framework. Comments about  obtained results, future developments and integration with current needs and new trends, are discussed.
